Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-03 article.tex
Polished Questions in the results section

% TODO: review the following questions:
What are the key factors/indicators of environmental sustainability in the australian winegrowing industry?
How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
What are the key factors that relate directly to environmental sustainability, and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?

@@

>>>>

% TODO: review the following questions:
What are the key factors/indicators of environmental sustainability in the australian winegrowing industry?
How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
What are the key factors that relate directly to environmental sustainability?
- and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?

@@

\section{Results}

    What are the factors of environmental sustainability in the Australian winegrowing industry?
        Purpose: Explore and understand the both the literature and industry perspectives on this.
        Results Literature review. Industry list of factors.

    How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
        Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
        Results: Use the agreed upon definitions to fully realise factors and their impact.

    What are the relationships between these factors in the Australian winegrowing industry?
        Purpose: Explore and understand the causal and correlated relationships among the factors.
        Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.

    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.

    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

Structuring the Results Section Based on These Questions:
Introduction to Results

    Content: Briefly restate the refined research questions.
    Explanation: Explain the approach to answering these questions using the BN model and CPT values.

Primary Factors Identification

Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?

    Content: Present the primary factors identified through your analysis.
    Data: Use the rigorous definitions and the generic BN to highlight these factors.
    Figures/Tables: Include a table or figure showing the key factors and their relative importance.

Quantitative Measurement and Analysis

Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?

    Content: Describe the methods used to measure and analyze the key factors.
    Data: Show measurements and analytical results from the CPT values in the specific BN models.
    Figures/Tables: Include charts or tables showing the measurements and analyses.

Relationships Between Factors

Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?

    Content: Discuss the direct and indirect relationships identified.
    Data: Present interaction diagrams or tables.
    Figures/Tables: Include a BN tree diagram illustrating these relationships.

Regional Variations

Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?

    Content: Compare the key factors and their impacts across different regions.
    Data: Present comparisons between the two specific BN models from different growers.
    Figures/Tables: Include figures comparing regional differences.

Scenario Analysis

Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?

    Content: Analyze the impact of different scenarios on environmental sustainability.
    Data: Use scenario-based BN queries to show changes in key factors and their impacts.
    Figures/Tables: Include charts or tables summarizing the scenario analysis results.

Example Framework for Presenting Results:
Introduction to Results

"The results of this study are structured to address five primary research questions aimed at understanding the key factors and their interactions affecting the environmental impact of vineyards in the Australian winegrowing industry. The analysis leverages Bayesian Network models to provide a comprehensive view of these factors and their contributions."
Primary Factors Identification

Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
Results:

    Identified Factors: Water usage, pesticide application, soil management, etc.
    Data Source: Defined terms provided by industry experts and the generic BN model.
    Figures: Table 1 shows the key factors and their relative importance derived from the BN analysis.

Quantitative Measurement and Analysis

Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
Results:

    Measurements: Quantitative analysis of key factors using CPT values from two specific BN models.
    Data Source: CPT values from BN models of two growers.
    Figures: Table 2 presents the measurements and analysis results.

Relationships Between Factors

Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
Results:

    Interactions: Direct and indirect relationships as illustrated by the BN model.
    Data Source: Generic BN model and specific models.
    Figures: Figure 1 illustrates the BN tree diagram showing these relationships.

Regional Variations

Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
Results:

    Regional Variability: Comparison of factors and impacts across regions using specific BN models.
    Data Source: BN models from two growers in different regions.
    Figures: Figure 2 compares the BN models for different regions.

Scenario Analysis

Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
Results:

    Scenarios: Impact analysis under different scenarios using BN models.
    Data Source: Scenario-based BN queries.
    Figures: Table 3 summarizes the scenario analysis results.

This refined approach ensures that your Results section directly addresses your research questions and clearly presents your findings. Let me know if there are specific details or sections you’d like further refined!
